\chapter{Measurement of the differential jet production cross section with respect to jet mass and transverse momentum in
Z + Jet events from pp collisions at $\sqrt{s}$ = 13 TeV}\label{chap:AN-18-240}

% copied from AN-18-240.tex

%\input{/Users/Om/Documents/thesis/AN-18-240/AN-18-240.tex}


Abstract.

We present a measurement of the differential jet production cross
section as a function of the jet mass and transverse momentum in
events with a Z + Jet topology, with and without a jet grooming
algorithm applied. For ungroomed jets, leading-order and next-to-leading order
QCD Monte Carlo programs are found to predict the jet mass
spectrum in the data reasonably well, with some disagreement
at very low and very high masses. 
For groomed jets, the agreement between the Monte Carlo programs and the data
improves overall, and extends lower in jet mass due to the removal of soft and
collinear portions of the jet. 
First-principles theoretical calculations of the groomed jet mass are in preparation by theorists to be compared
to the data. 




%%%
%%% INTRO
%%%


\section{Introduction}

\input{AN-18-240/introduction.tex}

%%%
%%%  DATA and MC 
%%%
\section{Data and MC}

\input{AN-18-240/dataandmc.tex}



%%%
%%%             TRIGGER
%%%
\section{Trigger}

The data are collected with single-lepton triggers, with muons (electrons) of $pt > 29 (37)$ GeV using the $IsoMu27$ ($Ele35_WPTight_Gsf$ $ || $ $ Photon200 $) triggers, as recommended by the muon (egamma) POG. All triggers used for this analysis are prescaled to 1. 




%%%
%%%                        RECO and SELECTION
%%%

\section{Reconstruction and Selection}


\input{AN-18-240/recoandsel.tex}

\section{Data to MC Comparisons}


\input{AN-18-240/datatomccomp.tex}




\section{Detector Response}

\input{AN-18-240/detresp.tex}



%%%%%%%%%%%


% MASS RESPONSE MATRICES

\input{AN-18-240/responsematrix_u.tex}


\input{AN-18-240/responsematrix_sdB0.tex}

% RHO RESPONSE MATRICES
\input{AN-18-240/rhoresponsematrix_u.tex}


\input{AN-18-240/rhoresponsematrix_sdB0.tex}


%PURITY and STABILITY

\input{AN-18-240/purity_u.tex}

\input{AN-18-240/purity_sdB0.tex}




\section{Uncertainties}

\input{AN-18-240/uncert.tex}


\section{Unfolding}

\input{AN-18-240/tunfolding.tex}

\section{Results}

\input{AN-18-240/results.tex}

\section{Summary}

In conclusion, we have presented a differential jet cross section measured in Z + Jet events in
bins of the ungroomed jet $\pt$ in conjunction with the ungroomed and groomed
jet mass (as well as dimensionless mass) using the ``soft drop'' (a.k.a. ``modified mass drop
tagger'') algorithm with 9 different combinations of parameters. 
The results are presented as the normalized cross section, normalized per reconstructed jet $\pt$ bin. 
Overall leading-order MC simulation agrees
reasonably well with the data within our uncertainties. 
Agreement below the Sudakov peak is slightly
worse than above. The application of a grooming algorithm
improves the overall precision, with larger improvement at low jet masses. 
This analysis improves over previous iterations by using various parameter values for the ``soft drop''
jet grooming algorithm, as well as by including an additional unfolding in both transverse momentum
and dimensionless mass, as was done by the ATLAS collaboration \cite{Aaboud:2017qwh} .





\appendix

\section{2016 data results}

This Appendix shows the distributions from the "Detector Response" through the "Results" sections of the main analysis note with only the 2016 data rather than the full Run 2 statistics seen in the main body of the note.



% MASS RESPONSE MATRICES

\input{responsematrix_u_2016.tex}


\input{responsematrix_sdB0_2016.tex}

% RHO RESPONSE MATRICES
%\input{rhoresponsematrix_u_2016.tex}


%\input{rhoresponsematrix_sdB0_2016.tex}


%PURITY and STABILITY

\input{purity_u_2016.tex}

\input{purity_sdB0_2016.tex}



\input{uncert_2016.tex}


\input{tunfolding_2016.tex}



\input{results_2016.tex}



%\section{Data and MC comparisons for soft-dropped jet masses}
\section{2017 data results}

This Appendix shows the distributions from the "Detector Response" through the "Results" sections of the main analysis note with only the 2017 data rather than the full Run 2 statistics seen in the main body of the note.



% MASS RESPONSE MATRICES

\input{responsematrix_u_2017.tex}


\input{responsematrix_sdB0_2017.tex}

% RHO RESPONSE MATRICES
%\input{rhoresponsematrix_u.tex}


%\input{rhoresponsematrix_sdB0.tex}


%PURITY and STABILITY

\input{purity_u_2017.tex}

\input{purity_sdB0_2017.tex}



\input{uncert_2017.tex}


\input{tunfolding_2017.tex}



\input{results_2017.tex}




\section{2018 data results}

This Appendix shows the distributions from the "Detector Response" through the "Results" sections of the main analysis note with only the 2018 data rather than the full Run 2 statistics seen in the main body of the note.



% MASS RESPONSE MATRICES

\input{responsematrix_u_2018.tex}


\input{responsematrix_sdB0_2018.tex}

% RHO RESPONSE MATRICES
%\input{rhoresponsematrix_u_2016.tex}


%\input{rhoresponsematrix_sdB0_2016.tex}


%PURITY and STABILITY

\input{purity_u_2018.tex}

\input{purity_sdB0_2018.tex}



\input{uncert_2018.tex}


\input{tunfolding_2018.tex}



\input{results_2018.tex}




